Lab2

### 2021-08-06 notebooks/Draft_Report.Rmd

---

#### Operationalization of additional variables
To enrich our model and limit OVB, we brainstormed a number of additional variables that could affect travel rates during COVID. For one, we looked at how COVID affected the county, $$through the unemployment rate$$. We also looked at age, gender, income demographics. Then, in addition to income demographics, we focused on percent of younger folks, as defined as those younger than 17 and older folks as defined as those older than 65 because of the nature of how COVID affects an individual.

@@

\clearpage

@@

First, we consider the models holistically. Here are some of our observations:
* In `Model 1`, all of our variables are extremely significant, though in the opposite direction as expected. We would expect an inverse relationship between COVID and travel, though it seems that this model is producing a positive relationship.
* In `Model 2`, when county density is factored in, the presence of COVID seems to have less positive of an effect on travel and that higher density counties see more travel.
* In `Model 3` with age factored in, we see that actually the most statistically significant effect on long trips are median income of the household and presence of kids under 17.
* In terms of $R^2$ and RSE, we are improving with each model.
* The addition of our chosen parameters for each following model is also statistically better than the previous, as indicated by the F statistic.

>>>>

#### Operationalization of additional variables
To enrich our model and limit OVB, we brainstormed a number of additional variables that could affect travel rates during COVID-19. For one, we looked at how COVID-19 affected the county, $$through the unemployment rate$$. We also looked at age, gender, income demographics. Then, in addition to income demographics, we focused on percent of younger folks, as defined as those younger than 17 and older folks as defined as those older than 65 because of the nature of how COVID-19 affects an individual.

@@

@@

First, we consider the models holistically. Here are some of our observations:
* In `Model 1`, all of our variables are extremely significant, though in the opposite direction as expected. We would expect an inverse relationship between COVID and travel, though it seems that this model is producing a positive relationship.
* In `Model 2`, when county density is factored in, the presence of COVID seems to have less positive of an effect on travel and that higher density counties see more travel.
* In `Model 3` with age factored in, we see that actually the most statistically significant effect on long trips are median income of the household and presence of kids under 17.

* In terms of $R^2$ and RSE, we are improving with each model.
* The addition of our chosen parameters for each following model is also statistically better than the previous, as indicated by the F statistic.

$$RECHECK THIS SECTION FOR VALUES$$
```{r calc. coeff percents}
#Model 1
#when you compare a coeff for non-log x to a log y:
(1-exp(coef(model1)["is_rural"]))*100
#For every percent increase in x 'is rural', you get a #% outcome in number of long trips.

#Model 2
(1-exp(coef(model2)["is_rural"]))*100
#Model 3
(1-exp(coef(model3)["is_rural"]))*100

#Same for income

#Model 2
(1-exp(coef(model2)["log(median_income + 1)"]))*100
#Model 3
(1-exp(coef(model3)["log(median_income + 1)"]))*100

#Same for density

#Model 2
(1-exp(coef(model2)["log(density)"]))*100
#Model 3
(1-exp(coef(model3)["log(density)"]))*100

#Same for age 17 & 65
#Model 3
(1-exp(coef(model3)["log(lt17)"]))*100
(1-exp(coef(model3)["log(gt65)"]))*100
```

### 2021-08-06 src/data/DataCleaning.Rmd

```{r merge limited model dataframe}
d <- merge(x = age_f, y = d, by = c("county"))
d <- d %>% drop_na()

@@

```{r clean unemployment data}
d <- d %>%
  select(
    county,
    long_trip,
    cases,
    deaths,
    median_income,
    total_pop,
    is_rural,
    unemployed,
    density,
    pct_lt17,
    pct_gt65,
    in_poverty
  )
knitr::kable(head(d))
```

>>>>

```{r merge limited model dataframe}
d <- merge(x = age_f, y = d, by = c("county"))
d <- d %>% rowwise() %>%
  mutate(
    lt17 = as.integer(0.01 * pct_lt17 * total_pop),
    gt65 = as.integer(0.01 * pct_gt65 * total_pop)
  )
d <- d %>% drop_na()

@@

```{r clean unemployment data}
d <- d %>%
  select(
    county,
    long_trip,
    cases,
    deaths,
    median_income,
    total_pop,
    is_rural,
    unemployed,
    density,
    lt17,
    gt65,
    in_poverty
  )
knitr::kable(head(d))
```
